Some Nice Title Goes Here, Eventually\ldots

### 2014-08-30 doc/tacs2014/article.tex
Document overview added to introduction, additional references in section II.

	\section{Introduction}

@@

	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms; notable successful techniques in
	widespread use today include support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty} \cite{tappert1990state}

	\section{Problem description}

@@

	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
	and that other characteristics must be taken into account, it becomes apparent that the same designs that
	yields highly accurate results on the western alphabet will not perform satisfactory when applied to asian character recognition, \cite{tappert1990state}
	unless it relies on complex, computationally expensive techniques such as for instance ``deep'' neural networks. \cite{ciresan2012multi}

	In this work, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
	thereby reducing the complexity of each undertaking. The design scheme also permits replacing classification strategies,
	and facilitates the parallelization of network training.

	\section{Previous work}

@@

	\section{Proposed solution}

@@

	\section{Experiments}

@@

	\section{Preliminary results}

@@

	\section{Conclusions}

@@

	\section{Future work}

>>>>

	\section{Introduction}
	\label{sec:introduction}

@@

	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms; notable successful techniques in
	widespread use today include support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty, tappert1990state}

	This paper documents a work in progress on the topic intelligent handwriting recognition of Japanese characters.
	The remainder of the article is structured as follows:
	In section \ref{sec:problem_description} we present the Japanese writing system and outline the primary issues with handwriting recognition for asian script;
	thereafter in \ref{sec:previous_work}, we discuss some notable advances aimed at solving various aspects of the aforementioned problems.
	An explanation of the proposed solution is given in section \ref{sec:proposed_solution}, and an initial, experimental implementation is described in \ref{sec:experiments}
	-- the results of which are recorded and examined in section \ref{sec:experiment_results}. Finally, conclusions and future work is presented in sections
	\ref{sec:conclusions} and \ref{sec:future_work}, respectively.

	\section{Problem description}
	\label{sec:problem_description}

@@

	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
	and that other characteristics must be taken into account, it becomes apparent that the same designs that
	yields highly accurate results on the latin alphabet will not perform satisfactory when applied to asian character recognition \cite{tappert1990state, liu2004online}
	-- unless it relies on complex, computationally expensive techniques such as for instance ``deep'' neural networks. \cite{ciresan2012multi}

	In continuation, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
	thereby reducing the complexity of each undertaking. The design scheme also permits replacing classification strategies,
	and facilitates the parallelization of network training.

	\section{Previous work}
	\label{sec:previous_work}

@@

	\section{Proposed solution}
	\label{sec:proposed_solution}

@@

	\section{Experiments}
	\label{sec:experiments}

@@

	\section{Preliminary results}
	\label{sec:experiment_results}

@@

	\section{Conclusions}
	\label{sec:conclusions}

@@

	\section{Future work}
	\label{sec:future_work}
